---
title: "Brazilian Demoghaphics by Cities - v1.1"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    social: menu
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(leaflet)
library(ggplot2)
library(mgcv)

# Load dataset
br_demographics <- read.csv("BRAZIL_CITIES.csv", header = TRUE, sep = ";")

```

Inputs {.sidebar}
=======================================================================

```{r}

states <- names(table(br_demographics$STATE))
states <- append(states,"All", length(states))


selectInput("state", "State", states, selected = "All", multiple = FALSE)

sliderInput("population", "Population", min=min(br_demographics$IBGE_RES_POP, na.rm = TRUE), max=max(br_demographics$IBGE_RES_POP, na.rm = TRUE), value=c(min(br_demographics$IBGE_RES_POP, na.rm = TRUE),max(br_demographics$IBGE_RES_POP, na.rm = TRUE)), step = 1000)

sliderInput("idh", "IDH", min = min(br_demographics$IDHM, na.rm = TRUE), max=max(br_demographics$IDHM, na.rm = TRUE), value=c(min(br_demographics$IDHM, na.rm = TRUE),max(br_demographics$IDHM, na.rm = TRUE)), step = 0.001)

sliderInput("companies", "Companies", min = min(br_demographics$COMP_TOT, na.rm = TRUE), max=max(br_demographics$COMP_TOT, na.rm = TRUE), value = c(min(br_demographics$COMP_TOT, na.rm = TRUE),max(br_demographics$COMP_TOT, na.rm = TRUE)), step = 1)

sliderInput("gdp", "GDP", min = min(br_demographics$GDP, na.rm = TRUE), max=max(br_demographics$GDP, na.rm = TRUE), value = c(min(br_demographics$GDP, na.rm = TRUE),max(br_demographics$GDP, na.rm=TRUE)), step = 1)


```

Dashboard
=====================================

```{r}

mapState <- reactive({
   if(input$state != "All"){
        subset(br_demographics, STATE == input$state)
   } else {
        br_demographics 
   }
})


mapPeople <- reactive({
     subset(mapState(), (IBGE_RES_POP >= input$population[1] & IBGE_RES_POP <= input$population[2]))
})



mapIDH <- reactive({
     subset(mapPeople(), (IDHM >= input$idh[1] & IDHM <= input$idh[2]))
})

mapCompanies <- reactive({
     subset(mapIDH(), (COMP_TOT >= input$companies[1] & COMP_TOT <= input$companies[2]))
})

mapGDP <- reactive({
     subset(mapCompanies(), (GDP >= input$gdp[1] & GDP <= input$gdp[2]))
})

```

Row
-------------------------------------

### Total Population {.value-box}

```{r}
# Emit the download rate
renderValueBox({
  valueBox(
    value = sum(mapGDP()$IBGE_RES_POP),
    icon = "fa-users",
    color = "primary"
  )
})

```


### Companies {.value-box}

```{r}
# Emit the download rate
renderValueBox({
  valueBox(
    value = sum(mapGDP()$COMP_TOT),
    icon = "fa-money",
    color = "green"
  )
})

```


### IDH Range {.value-box}

```{r}
# Emit the download rate
renderValueBox({
  valueBox(
    value = paste(min(mapGDP()$IDHM), " - ",max(mapGDP()$IDHM)),
    icon = "fa-heartbeat",
    color = "Orange"
  )
})

```


### GDP Range {.value-box}

```{r}
# Emit the download rate
renderValueBox({
  valueBox(
    value = paste(min(mapGDP()$GDP), " - ",max(mapGDP()$GDP)),
    icon = "fa-line-chart",
    color = "brown"
  )
})

```



Row
------------------------------------
   
### Map

```{r}

renderLeaflet({

     if(nrow(mapGDP()) == 0){
          return(NULL)
     }
     
     
     leaflet(mapGDP()) %>%
          addTiles() %>%
          addCircles(weight = 2, radius = sqrt(mapGDP()$IBGE_RES_POP) * 30, popup = 
               paste("<b>City: </b>", mapGDP()$CITY, " - ", mapGDP()$STATE, "<br>",
                     "<b>Population: </b>",mapGDP()$IBGE_RES_POP, "<br>",
                     "<b>IDH:</b>", mapGDP()$IDHM, "<br>",
                     "<b>Companies: </b>", mapGDP()$COMP_TOT, "<br>",
                     "<b>GDP: </b>", mapGDP()$GDP), 
               group="int")

})

```  


Help
=====================================

### Help

#### How to use?
- Select State or All to view all Country.
- Select Ranges to view results in Dashboard.
- Circles represents the amouth of population for each city.
- Click in circles to view some detais about city.


#### General Info
- Developed by: **Expedito Pinto de Paula Junior**
- Course: **Developing Data Products**
- Description: This Data Product it was developed using *flexdashboard* and *shiny*
- Dataset Source: The dataset used from [kaggle -  brazilian cities](https://www.kaggle.com/crisparada/brazilian-cities)
- Version: 1.1
- Date: Nov 20, 2020