---
title: "Brazilian Demographic Project"
author: "Expedito Pinto de Paula Junior"
date: "11/20/2020"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Context

Brazil is the world's fifth-largest country by area, with 8.5 million square kilometer, and the fifth most populous, with over 208 million people.

The Federative Republic of Brazil is composed of the union of the 26 states, the Federal District, and the 5,570 municipalities.

This dataset is a compilation of several publicly available information about Brazilian Municipalities.

## Synoposis

The objectives of this project are:

1. Analyse Brazilian demoghaphics information based in population size, IDH (Human Development Index), Number of Companies and Gross Development Product.
2. Use map based visualization to analyse data.
3. Enable user self capability to analyse and visualize data.

## Brazilian Cities Dataset

The Dataset created by **Cristiana Parada** in Version 7.

The data was retrieved from several websites, processed and merged all data by city name, resulting in 79 fields for every city.

The Dataset is available in link bellow:

[Brazilian Cities Dataset](https://www.kaggle.com/crisparada/brazilian-cities)


## Brazilian Demographics Dashboard

The [Brazilian Demographics Dashboard](https://speed-junior.shinyapps.io/ddp3) it was developed using **shiny** apps, **flexdashboard** library and **leafleat** maps.

In the Tab Help it's possible to find more information about how to use the App and General Information about version and author.

## HDI Education Index VS HDI GNI Index in all cities in Brazil

```{r plot1, message=FALSE, warning=FALSE}
library(plotly)
library(ggplot2)
brcities <- read.csv("BRAZIL_CITIES.csv", header = TRUE, sep = ";")
fig <- plot_ly(brcities,x=~IDHM_Educacao, y=~IDHM_Renda, type = "scatter", color = ~STATE, mode = "markers", marker = list(opacity = 0.7) ,text = ~paste("City:", CITY))
fig
```

## HDI Education Index VS HDI GNI Index in all cities in Brazil

```{r plot2, message=FALSE, warning=FALSE}
fig2 <- plot_ly(brcities,x=~IDHM_Educacao, y=~IDHM_Renda, type = "scatter", color = ~CAPITAL, mode = "markers", marker = list(opacity = 0.5), text = ~paste("City:", CITY))
fig2
```

## Some Findings

### The 5 best cities in relation btw HDI and GNI are: 
     1. São Caetano do Sul
     2. Niterói
     3. Vitoria
     4. Florianópolis
     5. Santos

### The 5 Best Capitals in relation btm HDI and GNI are:
     1. Vitória
     2. Florianópolis
     3. Brasilia
     4. Curitiba
     5. Belo Horizonte


## Conclusion

* Analysing Brazilian demoghaphics information is possible to understand that most of the IDHs, GDPs and amount of companies are near the big cities.
* Most of the cities in Brazil has less than 400,000 people.
* The GDP Range is to large as IDH Range this impacts in growing planing for the country.
* Based in the Dataset, several further analysis are possible to be realized.
